---
title: "Lab 4: Introduction to linreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab 4: Introduction to linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## 1.Introduction

This vignette provides a brief introduction to the `linreg()` function and shows how to use the methods available for objects of class `linreg`.

## 2.Load the package

```{r setup}
library(lab4advr)
```
## 3.Fit a linear regression model

In this example, we use the `iris` dataset to fit a linear regression
```{r}
data(iris)

#model <- linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris)
model <- linreg(Petal.Length~Species, data = iris)
```

## 4.Coefficients
The estimated regression coefficients can be extracted using coef()
```{r}
coef(model)
```

## 5.Residuals
The residuals can be obtained using resid().
```{r}
resid(model)
```

## 6.Predicted values
The fitted values can be obtained using pred()
```{r}
pred(model)
```

## 7.Summary
A summary of the model can be displayed using summary().
```{r}
summary(model)
```

## 8.Diagnostic plots
Diagnostic plots can be produced using plot().
```{r, warning=FALSE, message=FALSE}
plot(model)
```
